Learning Auditory Similarities Between Instrumental Playing Techniques

### 2020-04-04 paper/paper.tex
provide feedback on methods section
renamed method subsections

\begin{figure}[h!]
\caption{\csentence{Sample scattering}
Same 3 sounds spec + scatt.}
\end{figure}

@@

\subsection*{Scattering transform}
\label{sec:scattering}

% cite Lostanlen PhD dissertation. classification results on Medley-solos-DB. suggests that JTFS is competitive wrt deep learning techniques even in the large data regime (500-5000 samples per class).

@@

The definition of the scattering transform in terms of wavelet decompositions and modulus nonlinearities presents several advantages.
On the computational side, the critical bandwidth guarantees of wavelet transforms allows us to judiciously subsample the output, resulting in a lower-dimensional representation compared to the cortical representations.
The scattering transform also satisfies the aforementioned stability conditions, providing a guarantee that slightly deforming a signal only results in a negligible change in its scattering transform.
Furthermore, we may calculate the scattering transforms of several model signals, including amplitude-modulated harmonic sounds and noise excitations \cite{anden2012scattering,anden2014tsp}, frequency-modulated sinusoids (e.g., chirps) \cite{anden2012scattering,anden2019tsp}, and beating phenomena \cite{anden2014tsp}.
They have also enjoyed success in several audio classification and similarity retrieval tasks \cite{anden2011multiscale,bauge2013representing,anden2014tsp,anden2019tsp,lostanlen2018jasmp,lostanlen2018extended}.
%\ja{Need to flesh out the above with some equations.
%We're no longer talking to biologists, so we don't need to be afraid.}

\subsection*{Similarity weighting}
\label{sec:weighting}

@@

We now use the consensus clustering to reweight the similarity between feature vectors (either MFCCs or scattering transforms).
For this, we use the \emph{large margin nearest neighbor} (LMNN) metric learning algorithm \cite{weinberger2006distance, weinberger2009distance}.
This approach constructs a positive semi-definite weighting matrix $L$ such that the distance $\|Lx - Ly\|$ best classifies a set of points into a fixed clustering assignment.

\section*{\nmu Machine listening experiments}
\label{sec:results}

The processing pipeline presented in Figure \ref{fig:pipeline} addresses the problem of conditioning a timbre space using perceptual judgments of timbral similarity.
The relevance of the many design choices that had to be made are addressed in this section using an experimental protocol that considers a dataset of audio that will be given as input to the processing pipeline and one metric used for evaluating its performance under a given experimental setting.
\ja{This last sentence is quite vague.
What are we trying to say?}%

% TODO VL: organize design choices.
% (1) temporal support
% (2) time-frequency scattering / time scattering
% (3) learning / no learning

\subsection*{Data}

>>>>

@@

\subsection*{Joint time--frequency scattering transform}
\label{sec:scattering}

@@

The definition of the scattering transform in terms of wavelet decompositions and modulus nonlinearities presents several advantages.
On the computational side, the critical bandwidth guarantees of wavelet transforms allows us to judiciously subsample the output, resulting in a lower-dimensional representation compared to the cortical representations.
The scattering transform also satisfies the aforementioned stability conditions, providing a guarantee that slightly deforming a signal only results in a negligible change in its scattering transform.
Furthermore, we may calculate the scattering transforms of several model signals, including amplitude-modulated harmonic sounds and noise excitations \cite{anden2012scattering,anden2014tsp}, frequency-modulated sinusoids (e.g., chirps) \cite{anden2012scattering,anden2019tsp}, and beating phenomena \cite{anden2014tsp}.
They have also enjoyed success in several audio classification and similarity retrieval tasks \cite{anden2011multiscale,bauge2013representing,anden2014tsp,anden2019tsp,lostanlen2018jasmp,lostanlen2018extended}.
%\ja{Need to flesh out the above with some equations.
%We're no longer talking to biologists, so we don't need to be afraid.}
% TODO: avoid citing the same papers over and over

\begin{figure}
\caption{\csentence{Sample scattering}
Same 3 sounds spec + scatt.
% TODO figure + caption
}
\end{figure}

\subsection*{Metric learning with large-margin nearest neighbors (LMNN)}
\label{sec:weighting}

@@

We now use the consensus clustering to reweight the similarity between feature vectors (either MFCCs or scattering transforms).
For this, we use the \emph{large margin nearest neighbor} (LMNN) metric learning algorithm \cite{weinberger2006distance, weinberger2009distance}.
This approach constructs a positive semi-definite weighting matrix $L$ such that the distance $\|Lx - Ly\|$ best classifies a set of points into a fixed clustering assignment.
% TODO: this section needs more detail. In particular, it is worth discussing the role of Euclidean distances as an "initial guess" for LMNN. (this is unlike MLR, for example).

\section*{\nmu Results}
\label{sec:results}

This sec
% TODO VL: organize design choices.
% (1) temporal support
% (2) time-frequency scattering / time scattering
% (3) learning / no learning

\subsection*{Semi-supervised label propagation}
